### 2024-06-09 index.qmd
20240608 - clean up
20240608 - petersenlab package

::: {.content-hidden unless-format="pdf"}

@@

:::

::: {.content-hidden when-format="pdf"}

# Preface {#sec-preface}

:::

@@

In terms of my `R` and statistics background, I have published many [peer-reviewed publications](https://developmental-psychopathology.lab.uiowa.edu/publications) that employ advanced statistical methods, have published a [book on psychological assessment](https://www.routledge.com/9781032413068) that includes applied examples in `R`, and have published [an `R` package](https://cran.r-project.org/web/packages/petersenlab/index.html) on the Comprehensive R Archive Network (CRAN).

>>>>

@@

@@

In terms of my `R` and statistics background, I have published many [peer-reviewed publications](https://developmental-psychopathology.lab.uiowa.edu/publications) that employ advanced statistical methods, have published a [book on psychological assessment](https://www.routledge.com/9781032413068) that includes applied examples in `R`, and have published [the `petersenlab` `R` package](https://cran.r-project.org/web/packages/petersenlab/index.html) on the Comprehensive R Archive Network (CRAN).
